---
title: "Video Engagement Report"
author: "Group 6"
output: html_document
params:
    display: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = params$display)
```

# Introduction

For our group project, we will complete the following tasks:

1. Create a table that shows video engagement for each week.   
2. Create a visual that displays the information from the engagement table.   
3. Create a summary table showing the mean views per video in each topic.     
4.  Build a model for predicting engagement based on topic, video_number, length.  


The element of customization of our workflow that will be implemented for this report is to use parameterization to create flexible output of the final product.

The final product will include 2 to 3 tables and 1 to 2 figures. The first table will show each video and show the level of engagement in descending order. The figure will show the timeline on the x-axis and number of views on the y-axis so we can see the temporal trend of engagement. The second table will display the number of videos within each topic and the mean views per video in each topic. The predictive model will be shown as a formula and resulting table to show the predicted value of the coefficients. 

The parameterization allows for the inclusion or exclusion of the code in the html rendered report.

# Data set


```{r, load-data, message=FALSE}
here::i_am("engagementReport.Rmd")
engagement <- readRDS(
  file = here::here("output/data_clean.rds")
)

# maybe include code to display metadata here
```

# 1) Katie's Analysis
### Average number of views on weekly pre-read content.
```{r katie}
 katie_1 <- readRDS(
   file = here::here("output/katie1.rds")
 )
 
katie_1
```

This figure represents the average number of views for the pre-read content during any given week of INFO550. This plot displays the average number of views, representing the number of students that are engaging with the course materials before class time. The error bars represent the standard deviation among the videos that are made available for that specific week.

# 2) Xinyue's Analysis  
A linear model was fitted to test the potential factors on unique viewers. Week, video number and topics are re-categorized.   

### Summary of Linear model
```{r xinyue}
xinyue_2 <- readRDS(
  file = here::here("output/xinyue2.rds")
 )
#
xinyue_2
```

The results of the linear model are displayed above.  
2 topics are not defined because of singularities.  

# 3) Uzoamaka's Analysis
### Table for video count and mean views by topic
```{r uzoamaka}
uzoamaka_1 <- readRDS(
  file = here::here("output/uzoamaka1.rds")
)
 
uzoamaka_1
```

The above table shows each unique video topic, the topic's mean views per video, and the video count per topic.


# 4) Tiffany's Analysis
### Total Views per Topic
```{r tiffany}
tiffany_1 <- readRDS(
   file = here::here("output/tiffany1.rds")
 )
 
tiffany_1
```

The above figure shows the total amount of views that each topic received for all of that topic's videos.